Economic Theory of Fertility Explains Modern Natural Selection

### 2020-12-01 why-negative-selection.Rmd
trivia

Our results suggest that polygenic scores may directly correlate with
age at first live birth. Figure \@ref(fig:plot-age-flb-dv) plots
estimated effect sizes from bivariate regressions for respondents, and
Figure \@ref(fig:plot-age-birth-parents-dv) does the same for their
parents. Effect sizes are reasonably large. They are also very highly
correlated across generations. Effect sizes of PGS on father's age at
own birth, and on own age at first live birth, have a correlation of
`r cor_flb_fath`; for mother's age and own age it is `r cor_flb_moth`

>>>>

Our results suggest that polygenic scores may directly correlate with
age at first live birth. Figure \@ref(fig:plot-age-flb-dv) plots
estimated effect sizes from bivariate regressions for respondents, and
Figure \@ref(fig:plot-age-birth-parents-dv) does the same for their
parents. Effect sizes are reasonably large. They are also very highly
correlated across generations. Effect sizes of PGS on father's age at
own birth, and on own age at first live birth, have a correlation of
`r cor_flb_fath`; for mother's age and own age it is `r cor_flb_moth`.
